---
title: "Resto Priors Experiment"
output: html_notebook
---

```{r}

library(tidyverse)
library(brms)
library(lme4)
library(lmerTest)
library(plotrix)
library(stringr)
library(readxl)
library(RColorBrewer)
library(Hmisc)
library(Cairo)
```

# Priors

Read in results from priors experiment and plot them against the price of the deal.

```{r}

d = read.csv("./data/priors.csv", comment = "#", header=F, col.names = c("time", "participant", "controller", "item", "element", "type", "group", "field_name", "field_value", "correct", "response_time"))

d = d %>%
  mutate(field_name = as.character(field_name)) %>%
  mutate(field_name = if_else(endsWith(field_name, "</p>"), "critical", field_name)) %>%
  select(-controller, -item, -element, -group, -correct, -response_time) %>%
  filter(field_name != "_REACTION_TIME_") %>%
  group_by(time, participant) %>%
    mutate(condition = type[1]) %>%
  ungroup() %>%
  select(-type) %>%
  spread(field_name, field_value) %>%
  filter(q1 == "Alex" & q2 == "no" & nativeq == "yes") %>%
  select(-q1, -q2, -nativeq) %>%
  drop_na() %>%
  separate(condition, sep="-", into=c("prior", "price")) %>%
  select(-prior, -time, -participant) %>%
  mutate(critical = as.numeric(as.character(critical))) %>%
  mutate(critical = (critical - 1) / 9) %>%
  mutate(price = as.numeric(as.character(price)))

d_means = d %>%
  #mutate(price=factor(price, levels=c("15", "16", "18", "20", "22", "24"))) %>%
  group_by(price) %>%
  summarise(m = mean(critical),
              s=std.error(critical),
              upper=m+1.96*s,
              lower=m-1.96*s) %>%
  ungroup()

ggplot() +
  #geom_smooth(data=d,  method = "lm", aes(x=price, y=critical, color=price), alpha=0.5) +
  
  stat_smooth(data=d, geom='smooth', alpha=0.2, method="lm", aes(x=price, y=critical, color=price)) +
  geom_point(data=d_means, stat="identity", position="dodge", size=4, aes(x=price, y=m, color=price)) +
  geom_errorbar(data=d_means, width=.1, alpha=1, aes(x=price, ymax=upper, ymin=lower, color=price)) +
  ylab("Liklihood of Ordering Both") +
  xlab("Cost of Deal") +
  ggtitle("Restaurant Priors Experiment") +
  theme(legend.position = 'none',
        axis.text=element_text(size=14),
        title=element_text(size=14),
        legend.text=element_text(size=14),
        axis.title=element_text(size=14),
        strip.text.x = element_text(size = 14))


#ggsave("priors.png",height=3.5,width=5)

```

## Interpretation Experiment

Read in results from interpretation experiment.

```{r}
d = read.csv("./data/interpretation.csv", comment = "#", header=F, col.names = c("time", "participant", "controller", "item", "element", "type", "group", "field_name", "field_value", "correct", "response_time"))

d = d %>%
  mutate(field_name = as.character(field_name)) %>%
  mutate(field_name = if_else(endsWith(field_name, "</p>"), "critical", field_name)) %>%
  select(-controller, -item, -element, -group, -correct, -response_time) %>%
  filter(field_name != "_REACTION_TIME_") %>%
  group_by(time, participant) %>%
    mutate(condition = type[1]) %>%
  ungroup() %>%
  select(-type) %>%
  spread(field_name, field_value) %>%
  separate(condition, sep="-", into=c("prior", "price")) %>%
  select(-prior, -time, -participant) %>%
  mutate(critical = as.numeric(as.character(critical)),
         price = as.numeric(as.character(price)),
         q2 = as.numeric(as.character(price))) %>%
  filter(q1 == "Alex" & (q2 == price) & nativeq == "yes") %>%
  drop_na() %>%
  select(-nativeq, -q1, -q2) %>%
  mutate(critical = (critical-1)/9)%>%
  mutate(model = "human")
```

Manually input the results of the best-fitting RSA model.

```{r}
d_rsa = data.frame(
  price = c(15, 16, 18, 20, 22, 24),
  critical = c(0.696, 0.647, 0.567, 0.564, 0.412, 0.193),
  model = c("RSA", "RSA", "RSA", "RSA", "RSA", "RSA"))

d_rsa_fix = data.frame(
  price = c(15, 16, 18, 20, 22, 24),
  critical = c(0.827, 0.793, 0.734, 0.732, 0.607, 0.381),
  model = c("RSA-fixed", "RSA-fixed", "RSA-fixed", "RSA-fixed", "RSA-fixed", "RSA-fixed"))

d = rbind(d, d_rsa, d_rsa_fix)

d = d %>%
  mutate(price=factor(price, levels=c("15", "16", "18", "20", "22", "24")))
```

Plot the human results against the fixed and free RSA results!

```{r}
d_avg = d %>%
  group_by(price, model) %>%
    summarise(m = mean(critical),
              s=std.error(critical),
              upper=m+1.96*s,
              lower=m-1.96*s) %>%
  ungroup()
  
d %>%
  ggplot() +
    stat_smooth(data = d, aes(x=d$price, y=d$critical), method="lm") +
    geom_point(data = d_avg, stat="identity", position="dodge", size=4, aes(x=price, y=m, ymax=upper, ymin=lower, color=model)) +
    geom_errorbar(data = d_avg, width=.1, alpha=1, aes(x=price, y=m, ymax=upper, ymin=lower, color=model)) +
    ylab("P(A --> A & B)") +
    xlab("Cost of Deal") +
    ggtitle("Interpretation") +
    #coord_cartesian(ylim=c(0,0.8)) +
    theme(legend.position = 'bottom',
          axis.text=element_text(size=14),
          title=element_text(size=14),
          legend.text=element_text(size=14),
          axis.title=element_text(size=14),
          strip.text.x = element_text(size = 14))
# Savin with device=cairo_pdf can help embed fonts better and may matter for some journal submission!
#ggsave("./images/interpret.pdf",height=3.5,width=5, device=cairo_pdf)
#ggsave("./images/interpret.png",height=3.5,width=5)


```

## Production

Read in the production data and plot it.

```{r}
d = read.csv("./data/production.csv", comment = "#", header=F, col.names = c("time", "participant", "controller", "item", "element", "type", "group", "field_name", "field_value"))

d = d %>%
  mutate(field_name = as.character(field_name)) %>%
  select(-item, -element, -group) %>%
  filter(field_name != "_REACTION_TIME_") %>%
  group_by(time, participant) %>%
    mutate(condition = type[1]) %>%
  ungroup() %>%
  filter(condition != "comprehension") %>%
  select(-type) %>%
  mutate(field_name = if_else(field_name == "“both”", "b", field_name)) %>%
  spread(field_name, field_value) %>%
  mutate(both = if_else(is.na(both), b, both)) %>%
  select(-b) %>%
  separate(condition, sep="-", into=c("world", "price")) %>%
  select(-time, -participant) %>%
  mutate(both = as.numeric(as.character(both)),
         exhaust = as.numeric(as.character(exhaust)),
         single = as.numeric(as.character(single)),
          price = as.numeric(as.character(price)),
         q2 = as.numeric(as.character(price))) %>%
  filter(q1 == "Alex" & (q2 == price) & nativeq == "yes") %>%
  select(-controller, -nativeq, -q1, -q2) %>%
  mutate(both = (both-1)/9,
         exhaust = (exhaust-1)/9,
         single = (single-1)/9) %>%
  mutate(sum = both + exhaust + single) %>%
  mutate(both = both / sum,
         exhaust = exhaust / sum,
         single = single / sum) %>%
  drop_na() %>%
  select(-sum) %>%
  gather(utt, val, both, single, exhaust)

d_means = d %>%
  group_by(world, price, utt) %>%
    summarise(m = mean(val),
              s=std.error(val),
              upper=m+1.96*s,
              lower=m-1.96*s) %>%
  ungroup()

d_both = d %>%
  filter(utt == "both")

d_single = d %>%
  filter(utt == "single")

d_exhaust = d %>%
  filter(utt == "exhaust")

d %>%
  ggplot() +
    #stat_smooth(data = d_both, aes(x=d$price, y=d$val), method="lm") +
    geom_point(data = d_means, stat="identity", position="dodge", size=3, aes(x=price, y=m, ymax=upper, ymin=lower, color=utt)) +
    geom_errorbar(data = d_means, width=.4, alpha=1, size=1, aes(x=price, y=m, ymax=upper, ymin=lower, color=utt)) +
    ylab("Utterance endorsement") +
    xlab("Cost of Deal") +
    ggtitle("Production Experiment") +
    facet_wrap(~world) +
    theme(legend.position = 'bottom',
          axis.text=element_text(size=14),
          title=element_text(size=14),
          legend.text=element_text(size=14),
          axis.title=element_text(size=14),
          strip.text.x = element_text(size = 14))
#ggsave("./images/elicitation.png", height=5,width=7)

```

### Statistics

Correlation between the cost of the deal and the utterance endorsement in the production experiment 

```{r}
d_stat = d %>%
  filter(utt == "both" & world == "single")
cor.test(d_stat$price, d_stat$val)

d_stat = d %>%
  filter(utt == "both" & world == "both")
cor.test(d_stat$price, d_stat$val)

d_stat = d %>%
  filter(utt == "single" & world == "single")
cor.test(d_stat$price, d_stat$val)

d_stat = d %>%
  filter(utt == "single" & world == "both")
cor.test(d_stat$price, d_stat$val)

d_stat = d %>%
  filter(utt == "exhaust" & world == "single")
cor.test(d_stat$price, d_stat$val)

d_stat = d %>%
  filter(utt == "exhaust" & world == "both")
cor.test(d_stat$price, d_stat$val)


```


